From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}

### 2024-01-07 title-page.tex
Updated title page

\title{From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}}

>>>>

\title{From Macrogenres to Microgenres via Relationality\footnote{Previous versions of this paper were presented at the University of Notre Dame Sociology Department Culture Workshop, the University of Arizona School of Sociology Brown Bag Series, the Duke University Department of Sociology Jensen Lecture Series, and as a keynote address at the Understanding Everyday Participation Project Closing Conference in Manchester, UK, where I received incisive feedback and questions from various audience members, most of which was incorporated into the first completed draft of the paper. Particular thanks go to Vaughn Schmutz and three \textit{Poetics} anonymous readers whose comments, suggestions, and challenges greatly improved the initial submission.}}
